Comparing the Jacobi Method and LLL lattice reduction algorithms for cryptographic applications

### 2014-12-01 report/paper.tex
GSO

\documentclass[10pt]{article}

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{color}
\newcommand{\my}[1]{{\color{blue} #1 }}

@@

@@

\section{Introduction}

\subsection{Results and Contributions}

@@

@@

This can be translated into a more formal definition\cite{SchnorrStanfordNotes}.\newline 
Let $b_1, b_2, ... b_n \in \mathbb{R}^m$ be linearly independent vectors. We call the additive subgroup

\[
L(b_1,b_2,...,b_n):= \displaystyle\sum_{i=1}^{n}b_i \mathbb{Z}
\] of $\mathbb{R}^m$, a lattice with basis $b_1,b_2,...,b_n$.

A lattice that has $b_1,b_2,...,b_n$ as basis vectors will be noted in matrix form as $B$ where each vector $b_i$ is a column of the matrix.

@@

\subsubsection{Random Lattice}
TODO: Still unsure about how to phrase it

@@

We define a \emph{nearly orthogonal lattice basis} $M$ of dimension $n$ and of bit length $k$ as a $nxn$ square matrix whose entries are $k$-bits picked at random. These lattices are frequently used for signal processing applications\cite{originalJacobiMethodLatticeBasisReduction}.

@@

\subsubsection{Orthogonality defect of a basis}
The \emph{orthogonality defect} of a basis $b_1, b_2,...,b_n$ of a lattice $L$ is defined by:
\[
    \text{OrthDefect}(L) := \frac{\displaystyle\prod^{n}_{i=1} \|b_i\| }{\det(L)}
\]

@@

\subsubsection{Hermite factor of a basis}
The \emph{Hermite Factor}, sometimes referred to as \emph{Hermite's constant} of basis vectors $b_1, b_2,...,b_n$ of a lattice $L$ is defined by

\[
    \text{HF}(L) := \frac{\|b_1\|}{\sqrt[n]{\det(L)}}
\]

@@

Given a basis of a $n$-rank integral lattice $L$, find $u \in L$ such that $\|u\| = \lambda_1 (L)$

@@

@@

LLL

>>>>

\documentclass[10pt]{article}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{color}
\newcommand{\my}[1]{{\color{blue} #1 }}

@@

\renewcommand{\vec}[1]{\mathbf{#1}}

@@

\section{Introduction}
\subsection{Results and Contributions}

@@

\subsection{Euclidean norm}

The Euclidean norm in $\mathbb{R}^n$ is a mapping from $\mathbb{R}^n \to \mathbb{R}$ that assigns the length to any vector of the space.

The mapping is defined for any vector of $\mathbb{R}^n$ as follows:

\[
\|\mathbf{b}\| = \sqrt{b_1^2 + b_2^2 + ... + b_n^2} 
\] 
as a consequence of the Pythagorean theorem

@@

This can be translated into a more formal definition\cite{SchnorrStanfordNotes}.\newline 
Let $\vec{b_1}, \vec{b_2}, ... \vec{b_n} \in \mathbb{R}^m$ be linearly independent vectors. We call the additive subgroup

\[
L(\vec{b_1}, \vec{b_2},..., \vec{b_n}):= \displaystyle\sum_{i=1}^{n} \vec{b_i} \mathbb{Z}
\] of $\mathbb{R}^m$, a lattice with basis $b_1,b_2,...,b_n$.

A lattice that has $\vec{b_1},\vec{b_2},...,\vec{b_n}$ as basis vectors will be noted in matrix form as $B$ where each vector $\vec{b_i}$ is a column of the matrix.

@@

\subsubsection{Random Lattice}

- lattice prime determinant p 
- unique HNF form
- 1 on the other places of the diagonal
- all entries under the p are smaller than P in absolute value.

--->

TODO: Still unsure about how to phrase it

@@

We define a \emph{nearly orthogonal lattice basis} $M$ of dimension $n$ and of bit length $k$ as a $n \times n$ square matrix whose entries are $k$-bits picked at random. These lattices are frequently used for signal processing applications\cite{originalJacobiMethodLatticeBasisReduction}.

@@

\subsubsection{Orthogonality defect of a basis}
The \emph{orthogonality defect} of a basis $\vec{b_1},\vec{b_2},...,\vec{b_n}$ of a lattice $L$ is defined by:
\[
    \text{OrthDefect}(L) := \frac{\displaystyle\prod^{n}_{i=1} \|\vec{b_i}\| }{\det(L)}
\]

@@

\subsubsection{Hermite factor of a basis}
The \emph{Hermite Factor} of basis vectors $\vec{b_1}, \vec{b_2},...,\vec{b_n}$ of a lattice $L$ is defined by

\[
    \text{HF}(L) := \frac{\|\vec{b_1}\|}{\sqrt[n]{\det(L)}}
\]

@@

Given a basis of a $n$-rank integral lattice $L$, find $\vec{u} \in L$ such that $\|\vec{u}\| = \lambda_1 (L)$

@@

\subsection{Gram-Schmidt orthogonalization process}
The \emph{Gram-Schmidt orthogonalization (\emph GSO) process} is a method for orthonormalising a set of vectors. Two vectors are orthonormal if they are both orthogonal and unit vectors.

The GSO process  can be defined recursively:
\[
\begin{cases}
\vec{b_1}^{\star} = \vec{b_i}  \\
\vec{b_i}^{\star} = \displaystyle\sum^{i-1}_{j=1} \mu_{i,j} \vec{b}
\end{cases}
\]

We define the Gram-Schmidt process as a method for orthnomomalising a set of vectors

the Gram–Schmidt process is a method for orthonormalising a set of vectors in an inner product space, most commonly the Euclidean space Rn

@@
